Universal Anonymous Signatures

### 2022-07-11 prism-backend/research/gsac/formal-uas.tex
Re-defining extract* and identify*, and adapting the rest of the properties.

\begin{description}
\item[$\fissue: (\usk,\attrs_{\scred},\attrs)
  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
  \famfissue, the issuance function defines the customized conditions required
  by the issuer to grant a credential over attributes \attrs, when requested by
  a user with secret key \usk, potentially leveraging a set of previously
  obtained credentials with attributes $\attrs_\scred$. \fissue returns $1$ to
  accept a request, $0$ to reject it.
\item[$\feval: (\usk,\attrs_{\scred},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, a set $\attrs_{\scred}$ of attributes in the
  credenetial used for signing, and message to be signed
  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
  is revealed in plaintext along with the signature, and $\yeval^1$ is
  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
  (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\attrs_{\scred},\msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials used for signing, and signed message, should be extractable by an
  opener. Its behaviour can be modulated by \Yeval, and it outputs a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

@@

Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
non-frameability. Where the first two have variants covering issuance and
signatures \todo{argue why issuance non-frameability does not make sense}.
%
However, as stated, we make use of some helper functions: \ExtractIssue and
\ExtractSign, which let us recover the witnesses used to produce a credential
or a signautre; and \IdentifyCred, and \IdentifySig, which associate credentials
and signatures to user identifiers \uid. Both types of functions have been used
before. For instance, the extraction-type are used in \cite{lnpy21,nps22}, and
functions of the identify-type are used in \cite{bfg+11,cdl16,gl19,dl21,fgl21}.
\todo{Re-write after done.} Indeed, it seems hard to avoid resorting to these
techniques when there is no traditional notion of opening.

\paragraph{Extractability.} %
We require that the witnesses used to produce each credential and signature can
be extracted from the corresponding \utrans and signature, respectively.
Furthermore, in order for our generalized notion of utility to have meaning, it
is required that, whenever a credential is issued by an honest issuer, or a
signature is accepted by \Verify, the extracted values produce the same value as
the chosen \fissue, \feval and \finsp functions. We capture this in the
\ExpExtractIssue and \ExpExtractSign games, which are crucial in the
unforgeability and non-frameability requirements.

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\todo{\OExtIss}}(\parm) \\
        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \vspace*{0.5em}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpExtractSign(1^\secpar)$}{%
        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
        \adv^{\todo{\OExtSig}}(\parm) \\
	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets        
        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
        \pcreturn 1 \\
	\pcreturn 0
      }
    \end{minipage}
  }
  \caption{Extractability experiments for \UAS schemes.}
  \label{fig:exp-uas-extract}
\end{figure*}

\paragraph{Identifiability.} %
On their own, the extractability properties only ensure that the produced
credentials and signatures have been produced by leveraging knowledge of some
witnesses. However, they do not establish any relationship between those
witnesses and the identity of their owner(s). While the way in which witnesses
are associated to user identifiers\footnote{We avoid the term \emph{user
    identity}, as that is very context-specific.} is dependent on the
construction, we impose some constraints that all schemes need to satisfy.
Namely, it must be possible to associate any credential (obtained from an honest
issuer), or any signature accepted by \Verify, to exactly one user identifier.

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\todo{\OIdCred}}(\parm) \\
        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        \suid \gets \IdentifyCred(\trap,\usk,\scred,\attrs_{\scred},\ipk_{\cred}) \\
        \pcif |\suid| \neq 1: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \vspace*{0.5em}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIdentifySign(1^\secpar)$}{%
        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\todo{\OIdSig}}(\parm) \\
	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets
        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
	\suid \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
	\pcif |\suid| \neq 1: \pcreturn 1 \\
	\pcreturn 0
      }
    \end{minipage}
  }
  \caption{Identifiability experiments for \UAS schemes.}
  \label{fig:exp-uas-identify}
\end{figure*}

\begin{definition}{(Identifiable credentials in \UAS)}
  \label{def:identify-cred-uas}  
  We define the advantage \AdvIdCred of $\adv$ against \ExpIdentifyCred as
  $\AdvIdCred=|\Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies identifiable credentials if, for any p.p.t. adversary
  $\adv$, \AdvIdentifyCred is a negligible function of $1^\secpar$.
\end{definition}

\begin{definition}{(Identifiable signatures in \UAS)}
  \label{def:identify-sig-uas}  
  We define the advantage \AdvIdSig of $\adv$ against \ExpIdentifySign as
  $\AdvIdSig=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies identifiable signature if, for any p.p.t. adversary
  $\adv$, \AdvIdSig is a negligible function of $1^\secpar$.
\end{definition}

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
      \exists \cred \in \scred~\suchthat~\IdentifyCred(\trap,\usk,
      \attrs_{\cred},\cred,\ipk) = 0: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      (\parm,\trap) \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\suchthat~
      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
      \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

\begin{definition}{(Unforgeable issuance of \UAS)}
  \label{def:issue-forge-uas}  
  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
  \AdvForgeIssue is a negligible function of $1^\secpar$.
\end{definition}

\begin{definition}{(Unforgeable signing of \UAS)}
  \label{def:sign-forge-uas}  
  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
  \AdvForgeSign is a negligible function of $1^\secpar$.
\end{definition}

@@

\begin{figure}[htp!]
  \centering
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    \lor \yinsp \neq \yinsp': \pcreturn 1 \\   
    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk \land
    (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\uid]: \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

>>>>

\begin{description}
\item[$\fissue: (\usk,\attrs,\attrs_{\scred}) \rightarrow 0/1$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with secret key \usk,
  potentially leveraging a set of previously obtained credentials with
  attributes $\attrs_\scred$. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\usk,\attrs_{\scred},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, a set $\attrs_{\scred}$ of attributes in the
  credential used for signing, and message to be signed
  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
  is revealed in plaintext along with the signature, and $\yeval^1$ is
  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
  (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\attrs_{\scred},\msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials used for signing, and signed message, should be extractable by an
  opener. Its behaviour can be modulated by \Yeval, and it outputs a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

@@

Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
non-frameability. In addition, we make use of some helper functions:
\ExtractIssue and \ExtractSign, which let us recover the witnesses used to
produce a credential or a signautre; and \IdentifyCred, and \IdentifySig, which
associate credentials and signatures to user identifiers \uid. Both types of
functions have been used before. For instance, the extraction type are used in
\cite{lnpy21,nps22}, and functions of the identify type are used in
\cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
these techniques when there is no traditional notion of opening. Since, mostly
the unforgeability and non-frameability properties build on the extractability
and identifiability ones, we define them first. Then, we proceed with the usual
notions.

\paragraph{Extractability.} %
We require that the witnesses used to produce each credential and signature can
be extracted from the corresponding \utrans and signature, respectively.
Furthermore, in order for our generalized notion of utility to be sound, it
is required that, whenever a credential is issued by an honest issuer, \fissue
accepts the extracted witnesses; and whenever a signature is accepted by
\Verify, the extracted witnesses match the expected outputs by \feval and
\finsp. We capture this in the \ExpExtractIssue and \ExpExtractSign games, which
are crucial in the unforgeability and non-frameability requirements.

In the extractability variant for credentials, \ExpExtractIssue, the adversary
wins if it manages to get a credential from an honest user, such that the
issuance predicate \fissue rejects the extracted witnesses.
%
In the variant for signatures, \ExpExtractSign, the adversary wins if the
witnesses extracted from a signature accepted by \Verify make \feval and \finsp
output inconsistent values.
%
The oracles available in \ExpExtractIssue is, $\OExt \gets (\lbrace\HU,\CU
\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$. Note that,
honest issuers are required, as we rely on the availability of $\langle \Obtain,
\Issue \rangle$ transcripts to assist on the extraction. On the other hand,
for \ExpExtractSign, as we extract directly from signatures, honest issuers are
not a requirement, so the adversary is given access to $\ICORR$ too.

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\OExt}(\parm) \\
        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \vspace*{0.5em}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpExtractSign(1^\secpar)$}{%
        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
        \adv^{\OExt,\ICORR}(\parm) \\
	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets        
        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
        \pcreturn 1 \\
	\pcreturn 0
      }
    \end{minipage}
  }
  \caption{Extractability experiments for \UAS schemes.}
  \label{fig:exp-uas-extract}
\end{figure*}

\paragraph{Identifiability.} %
On their own, the extractability properties only ensure that credentials and
signatures have been produced by leveraging knowledge of some witnesses.
However, they do not establish any relationship between those witnesses and
users. While the actual technicalities of doing so is dependent on the
construction, we can, modelling-wise, enforce constraints that associate
user identifiers ({\uid}s, tracked by the game environment) with potential
witnesses. Namely, we require that it must be possible to associate any
credential (obtained from an honest issuer), or any signature accepted by
\Verify, with exactly one user identifier.

As for extractability, we define two variants. For credentials, in
\ExpIdentifyCred we require the adversary to output the identifier of a
credential obtained from an honest issuer. The adversary wins if, given the
witnesses extracted from the corresponding transcript, the \IdentifyCred helper
function outputs a set \suid of user identifiers with cardinality different than
$1$.
%
Similarly, for signatures, the adversary wins if it is able to produce a
signature from which the extracted witnesses, when passed to \IdentifySig,
output a set \suid of user identifiers with cardinality different than $1$.
%
The oracles are as in the extractability experiments. Namely, in the
\ExpIdentifyCred game, the adversary has access to $\OId \gets (\lbrace\HU,\CU
\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$, while in
\ExpIdentifySign it also has access to \ICORR. The same reasoning applies.

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\OId}(\parm) \\
        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        \pcfor \cred \in \scred: \\
        \pcind \suid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
        \pcind \pcif |\suid| \neq 1: \pcreturn 1 \\
        \pcind \pcif \suid~\textrm{differs from previous iterations}: \\
        \pcind \pcind \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \vspace*{0.5em}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIdentifySign(1^\secpar)$}{%
        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\OId,\ICORR}(\parm) \\
	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets
        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
	\suid \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
	\pcif |\suid| \neq 1: \pcreturn 1 \\
	\pcreturn 0
      }
    \end{minipage}
  }
  \caption{Identifiability experiments for \UAS schemes.}
  \label{fig:exp-uas-identify}
\end{figure*}

\begin{definition}{(Identifiable credentials in \UAS)}
  \label{def:identify-cred-uas}  
  We define the advantage \AdvIdCred of $\adv$ against \ExpIdentifyCred as
  $\AdvIdCred=|\Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme \emph{with extractable issuance} satisfies identifiable
  credentials if, for any p.p.t. adversary $\adv$, \AdvIdCred is a negligible
  function of $1^\secpar$.
\end{definition}

\begin{definition}{(Identifiable signatures in \UAS)}
  \label{def:identify-sig-uas}  
  We define the advantage \AdvIdSign of $\adv$ against \ExpIdentifySign as
  $\AdvIdSign=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme \emph{with extractable signatures} satisfies identifiable
  signature if, for any p.p.t. adversary $\adv$, \AdvIdSign is a negligible
  function of $1^\secpar$.
\end{definition}

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      \cid \gets \adv^{\Oforgeissue}(\parm) \\
      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
      \IK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
      \pccomment{\ExpIdentifyCred enforces the same \uid is
        returned for all \scred} \\
      \uid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
      \pcif \uid \notin \HU \cup \CU: 
      %\pcif % \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
%      \exists \cred \in \scred~\suchthat~\IdentifyCred(\trap,\usk,
%      \attrs_{\cred},\cred,\ipk_{\cred}) = 0: \\
      \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
  \label{fig:exp-uas-unfor-issue}
\end{figure}

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      (\parm,\trap) \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      % \pcreturn 1 \\
      % \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
      % \pcreturn 1 \\
      \uid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
      \uid' \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
      \pcif \uid \neq \uid' \lor \uid \notin \HU \cup \CU: \pcreturn 1 \\
      %\pcif \exists \cred \in \scred~\suchthat~
%      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
      % \pcreturn 1 \\
      % \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
      % \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

\begin{definition}{(Unforgeable issuance of \UAS)}
  \label{def:issue-forge-uas}  
  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme \emph{with identifiable credentials} has unforgeable issuance
  if, for any p.p.t. adversary $\adv$, \AdvForgeIssue is a negligible function
  of $1^\secpar$.
\end{definition}

\begin{definition}{(Unforgeable signing of \UAS)}
  \label{def:sign-forge-uas}  
  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme \emph{with identifiable signatures} has unforgeable signing if,
  for any p.p.t. adversary $\adv$, \AdvForgeSign is a negligible function of
  $1^\secpar$.
\end{definition}

@@

\begin{figure}[htp!]
  \centering
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
    % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
    % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
    \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk \land
    (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\uid]: \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}
